Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-05-17 PaperBCJ.tex
Habilitado Ingreso de Figuras
Start fo Convolutional Neural Networks

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial}

@@

Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} methos trough binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo \textit{et. al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop. The segmentation of weed and crops is not closed in Color Images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds. One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets
\\

@@

\section{Test}
%Codigo para la Implementacion del Algoritmo

@@

%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
 \bibitem{Cicco:Potena}
 M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Weed and Corn segmentation through Convolutional Neuronal Networks }

@@

Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} through binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo \textit{et. al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop.
\\

The segmentation of weed and crops is not closed to color images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds. One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets 
\\

@@

\begin{figure}
  \centering

  \caption{Some figure}
\end{figure}

\subsection{Convolutional Neuronal Network}
After the segmentation of the pictures have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}. Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants. 
\section{Test}
%Codigo para la Implementacion del Algoritmo

@@

%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
 \bibitem{Cicco:Potena}
 M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

 \bibitem{Razavian}
 A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
